Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-07 WRITEUP/ms.tex

\begin{abstract}
We study the dynamical properties of molecular clouds complexes and their temporal evolution in a prototypical galaxy 
at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation, 
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify molecular complexes (MC) and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in gas-rich galaxies in the local universe and at the peak epoch of cosmic \SF. 
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely results from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
% consistent with what has been found previously in higher resolution isolated simulation (our zoom-in sim here allows us to examine 
% the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM).
We compare the dynamics of MCs in \flower to those observed in the local Universe in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the 
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with ALMA will be useful to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

The growth of galaxies and their subsequent evolution are governed by the baryonic/baryon cycle ---
galaxies accrete gas from the intergalactic medium to fuel \SF (and feed their supermassive blackholes)
and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
The general consensus is that the growth of \highz galaxies are triggered/supported by massive
gas inflows from mergers and/or the cosmic web at early cosmic time, when the intergalactic
medium and galaxies themselves are more gas-rich in their star-forming molecular
gas contents compared to present-day galaxies.
% while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when
% the gravitational potential is still increasing), but their gas reservoirs
% are continuously being replenished.
These massive gas inflows in turn trigger gravitational instability, and thus, lead
to the formation of clouds/structures that are typically more massive and denser than those
observed in nearby galaxies, with cloud masses of $M_{\rm cloud}$\eq10$^9$\,\Msun
and sizes on sub-kpc scales (e.g. \citealt{Gabor13a, Hopkins14a, Inoue16a}).
%In cosmological context, minor mergers and external gas accretion can
%significantly impact on disc dynamics and clump formation
%(e.g. Bird et al. 2012, MNRAS, 420, 913; Kyziropoulos et al. 2016, MNRAS, 463, 2210).
Some theoretical works argues that it is in fact the
migration of such giant massive clumps that are responsible for contributing to the
buildup of the bulges of massive galaxies at \z$\sim$0 \citep[e.g.,][]{Ceverino10a}.

Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies 
since the cosmic dark ages.
Current consensus is that at higher redshifts, galaxies have higher 
star formation rates (SFR) \citep{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and 
smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to galaxies found in the local Universe, 
and thus, they are expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks. 
Since their metallicity and dust content are also expected to be lower as they are assembling, 
this affects the shielding of UV photons, heating and cooling mechanisms in this early systems. Such differences in turn can have a role in regulating the thermal and chemical structures of their ISM, and thus, their multi-phase ISM differ from nearby galaxies.
%
% talk about dynamical states of MCs of different galaxies? Even in the local universe, where the most detailed \obs can be done, we see variations in cloud properties in different galaxy populations (see e.g., Hughes10a, MNRAS, 406, 2065; Hughes+13b, ApJ, 779, 46), maybe also Meidt+13, apj, 779,45?. Thus, obvious to pose the question what are the dynamical states of the MCs of the first galaxies and how do they differ from nearby universe, and analogous to any of the nearby \galpop?
%

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, the ISM properties of \highz galaxies
have only been studied observationally in a handful of (strongly-lensed)
galaxies, using spatially resolved tracers such as
dust continuum, and CO and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that the ISM of $z$\ssim2 galaxies are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
On the other hand, the main source of reionization --- the first stars and first galaxies --- 
are ......
it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6
that dominates  \SF at the epoch of reionization which is responsible for producing the
ionizing photons that reionized the universe.

While ALMA has enabled the detections of
ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission in
normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Smit18a},
we are still far from mapping their molecular ISM.
In particular, their star-forming gas conditions, due to the stupid stingy ALMA TAC.
As such, we have undertaken a study, exploiting
state-of-the-art cosmological zoom-in hydrodynamic simulation
\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), to examine
the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$) lyman-break
galaxy (LBG).

@@

Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}.
Briefly, by \z$\sim$6, \flower is a LBG hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc. At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne. It is therefore a prototypical galaxy at \z$\sim$6.

@@

Given the stochasticity in the \SF history of \flower,
we show the scaling relations found for two particular snapshots/evolutionary stages of \flower
as examples in \Sec{singless} to illustrate the salient points of the discussion,
since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
most extreme variations in the cloud dynamics) --- one of which \flower is
actively accreting materials from its surrounding (top panel of \Fig{SFH})
and another of which \flower is undergoing
a starburst phase after a major merger (bottom panel of \Fig{SFH}).

\begin{figure*}[htbp]
\centering
\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/daisyleung2.pdf}
\caption{
	Top right: Star formation history of \flower.
	Projected stellar mass distribution of \flower during one of its accretion phases
	at its early stage of evolution {\it (a)}; during one of its major starburst phases
	after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
% f_gas history?
\label{fig:SFH}}
\end{figure*}

\subsection{Structure identification} \label{sec:method}
To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (aka k-d tree). It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across the tiles. 
In the customized version used for this study, we modify the function to enhance the stability of the code (which essentially means we fixed the bugs in order for it to actually work).

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
We note that this process is in essence similar to
identifying molecular structures based on the noise levels of surface density maps
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying
``clumps'' based on/after applying $\sigma$-clipping,
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind},
and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).
We note that, owing to the nature of \obs, such structures are identified 
in position-position-velocity (PPV) space in observational studies, whereas in simulations, one has the 
full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
Existing studies find a good correspondence in the dynamical properties extracted in
PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, 
Pan15a, Ibanez-Mejia16a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations). 
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

@@

In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see analysis presented by \citealt{Pallottini17b}).
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

>>>>

\begin{abstract}
We study the dynamical properties of molecular clouds complexes and their temporal evolution in a prototypical galaxy 
at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation, 
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify molecular complexes (MC) and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in gas-rich galaxies in the local universe and at the peak epoch of cosmic \SF. 
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
% consistent with what has been found previously in higher resolution isolated simulation (our zoom-in sim here allows us to examine 
% the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM).
We compare the dynamics of MCs in \flower to those observed in the local Universe in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the 
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with ALMA will be useful to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

The growth of galaxies and their subsequent evolution are governed by the baryon cycle ---
galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes)
and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
The general consensus is that the growth of \highz galaxies are triggered and supported by massive
gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves 
are more gas-rich in their star-forming molecular
gas contents compared to present-day galaxies.
% while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when
% the gravitational potential is still increasing), but their gas reservoirs
% are continuously being replenished.
These massive gas inflows in turn trigger gravitational instability and lead
to the formation of gas structures that are typically more massive and denser than those
observed in nearby galaxies, with masses of $M_{\rm cloud}$\eq10$^9$\,\Msun
and sizes on sub-kpc scales (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
Some theoretical works argue that the
migration of such giant massive clumps are responsible for contributing to the
buildup of the bulges of massive galaxies at \z$\sim$0 \citep[e.g.,][]{Ceverino10a}.

Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies 
since the cosmic dark ages.
Current consensus is that at higher redshifts, galaxies have higher 
star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and 
smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to those found in the local Universe.
The former are thus expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks. 
Since their metallicity and dust content are also expected to be lower as they are assembling, 
this affects the shielding of UV photons, heating and cooling mechanisms in these early systems. Such differences in turn 
affect the regulation of thermal and chemical structures of their ISM. 
Their multi-phase ISM and the dynamics of the star-forming molecular cloud complexes (MC)
are therefore expected to differ from nearby galaxies.
Even in the local Universe, where the most detailed \obs can be attained, variations in cloud properties have been 
observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
It is thus obvious and reasonable to pose the question: what are the dynamical states of the MCs of the first galaxies and 
how do they differ from the local Universe, and are they analogous to any seen in the local \galpop?
%

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, spatially resolved ISM properties of \highz galaxies
have only been examine observationally in a handful of (strongly-lensed)
galaxies, using tracers such as
dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that galaxies at $z$\ssim2 galaxies, close to the peak of cosmic \SF, are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
That said, it remains unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 --- 
at the epoch of reionization  ---
which is responsible for producing the
ionizing photons that reionized the Universe.

While ALMA has enabled the detections of
ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission in
normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Smit18a},
we are still far from mapping their molecular ISM due to the cosmological dimming.
As such, we have undertaken a study, exploiting
state-of-the-art cosmological zoom-in hydrodynamic simulation
\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), to examine
the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$) 
galaxy.

@@

Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}.
Briefly, by \z$\sim$6, \flower is a Lyman-break galaxy (LBG) hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne. It is therefore a prototypical galaxy at \z$\sim$6.

@@

Given the stochasticity in the \SF history of \flower,
we show the scaling relations found for two particular snapshots/evolutionary stages of \flower
as examples in \Sec{singless} to illustrate the salient points of the discussion,
since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
most extreme variations in the cloud dynamics) --- one of which \flower is
actively accreting materials from its surrounding 
and another of which \flower is undergoing
a starburst phase after a major merger (see \Fig{SFH}).

\begin{figure*}[htbp]
\centering
\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
	Star formation history of \flower (top right) and
	projected stellar mass distribution of \flower during one of its accretion phases
	at its early stage of evolution {\it (a)}; during one of its major starburst phases
	after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
% f_gas history?
\label{fig:SFH}}
\end{figure*}

\subsection{Structure identification} \label{sec:method}
To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (aka k-d tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles. 
In the customized version used for this study, we modify the function to enhance the stability of the code (which essentially means we fixed the bugs in order for it to actually work).

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
We note that this process is in essence similar to
identifying molecular structures based on the noise levels of surface density maps
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying
``clumps'' based on/after applying $\sigma$-clipping,
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind},
and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).
We note that, owing to the nature of \obs, such structures are identified 
in position-position-velocity (PPV) space, whereas in simulations, one has the 
full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
Existing studies find a good correspondence in the dynamical properties extracted in
PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, 
Pan15a, Ibanez-Mejia16a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations). 
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

@@

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the $r_{\rm 200}$ dark matter radius is $\sim$15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see calculation presented by \citealt{Pallottini17b}).
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.
